---
title: "Arcana Object Examples"
format: html
editor: visual
---

## Introduction

This document provides examples of creating and printing `arcana` objects, which represent cards from the Major Arcana of a tarot deck.

## Setup

First, we need to load the `arcana` package.

```{r}
# Load the package
library(devtools)
devtools::load_all()
library(arcana)
```

## Creating a Single Arcana Object

Here we create a single `arcana` object for "The Fool" card.

```{r}
# Create a new arcana object
the_fool <- new_arcana(,)
```

### Printing the Object

When we print the object, we should see a formatted output with the card's number, name, and keywords.

```{r}
# Print the object
print(the_fool)
```

## Creating Multiple Arcana Objects

We can also create a list of `arcana` objects. Here, we'll create the first three cards of the Major Arcana.

```{r}
# Create a list of arcana objects
first_three <- lapply(0:2, new_arcana)
```

### Printing the List

Printing the list will display the information for each card.

```{r}
# Print the list of objects
print(first_three)
```
